\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-22 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating Section IV

To numerically perform the proximal updates $\{\tilde{\varrho}_{k-1}^{i}\}_{i=1}^{N}\mapsto\{\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ for $k\in\mathbb{N}$, we implement an instance of the Algorithm 1 in \cite{caluya2019TAC}. This involves a dualization along
with an entropic regularization of the variational update \eqref{KineticProx}, and then solving the same using a fixed point recursion that is provably contractive; see \cite[Sec. V.B]{caluya2019TAC}. This enables a nonparametric computation of $\tilde{\varrho}_{k}^{i} \equiv \tilde{\varrho}_{k}\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right)$ for $i=1,\hdots,N$.

>>>>

To numerically perform the proximal updates $\{\tilde{\varrho}_{k-1}^{i}\}_{i=1}^{N}\mapsto\{\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ for $k\in\mathbb{N}$, we implement an instance of the Algorithm 1 in \cite{caluya2019TAC}. The algorithm involves a dualization along
with an entropic regularization of the variational update \eqref{KineticProx}, and then solving the same using a fixed point recursion that is provably contractive; see \cite[Sec. V.B]{caluya2019TAC}. This enables a nonparametric computation of $\tilde{\varrho}_{k}^{i} \equiv \tilde{\varrho}_{k}\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right)$ for $i=1,\hdots,N$.
